### 2021-07-03 docs/manuscript/manuscript.tex
Add closing statement
Improve closing statement
Include Gierer-Meinhardt

Among the new network topologies we report here, perhaps the most interesting
is the topology number 9, which is able to express the striped gene expression
pattern with only two genes and indeed expresses this pattern in both genes
(Fig~\ref{fig:topol9}).

@@

>>>>

Among the new network topologies we report here, perhaps one of the most
interesting ones is the topology number 9, which is able to express the striped
gene expression pattern with only two genes (Fig~\ref{fig:topol9}).
This topology is composed of a core that consists in the
Gierer-Meinhardt network~\cite{giererMeinh1972, meinhardt2000} known to
generate stripes and dots in bidimensional fields, and additional
interactions such as the self inhibition of gene A and the inhibition of the genes
by the morphogen. The Gierer-Meinhardt network consists in an activator of low
diffusivity (gene C) and an inhibitor with greater diffusivity (gene A). The additional
interactions of topology number 9 have the role of restricting the generation of
the expression band to a precise location.

@@

This work provides a catalog of GRNs that can be extended in future computational
and theoretical analysis and provides a foundation to design and build synthetic
regulatory networks or to identify new ones existing in nature.
